Consistency and variability in the development of children's drawings of object categories

### 2021-07-09 writing/Manuscript_June2021.Rmd
minor edits

```{r setup, include = FALSE}
library("papaja")
library(tidyverse)
library(here)
library(assertthat)
library(langcog)
library(ggthemes)
library(knitr)
library(lmerTest)
library(lme4)
library(xtable)
library(viridis)
```

@@

<!-- Overall, we replicated prior work [@long2021parallel], showing strong and consistent developmental changes in the recognizability of children's drawings across development across both geographical sites. In addition, children of all ages produced equally recognizable drawings across both drawing tasks, suggesting that working memory limitations are not amoung the primary factors that influence the recognizability of children's drawings. Finally, we found that children recruited  -->

@@

\
```{r load-tracing}
# import, standardized spliced session_ids, and join back together
# tracing IDs are read in by session_ids, so need these to join with metadata
tracing_thu <- read.csv(here::here('data/compiled/tracing_outputs/transformed_tracings.csv'))  %>%
  mutate(session_id =  paste0('Tsinghua_photodraw_',session_id)) %>%
  filter(site=='Tsinghua') %>%
  left_join(meta_thu, by=c('session_id','category')) %>%
  dplyr::select(-X.1, -X, -site.x, -filename.y) %>%
  rename(site = site.y, filename = filename.x)

@@

```{r check-drawing-time}
# drawing_time <- lmer(draw_duration ~ condition*scale(age_numeric)*site +
#                       (1 | unique_ids) +
#                       (1 | category),
#       data = d)
# 
# # frustratingly can't get anything with random slopes to converge!
# drawing_time_out = summary(drawing_time)

@@

```{r site-difference, include=FALSE, eval=FALSE, fig.env="figure", out.width = "\\textwidth", fig.pos = "H", fig.align = "center", fig.width=4, fig.height=4, fig.cap = "Proportion of drawings recognized as a function of the age of the child who completed each drawing and the geographical site they were tested at (San Jose vs. Beijing). Individual data points represent drawings within each condition by an individual participant and are slightly jittered. Error bars show bootstrapped 95 percent confidence intervals."}
cor_by_age_by_site <- d %>%
  group_by(unique_ids,category,age_numeric, site) %>%
  summarize(avg_cor = mean(prop_correct)) %>%
  group_by(age_numeric, site) %>%
  multi_boot_standard(col = "avg_cor")

cor_by_age_by_site_by_indiv <- d %>%
  group_by(unique_ids,category,age_numeric, site) %>%
  summarize(avg_cor = mean(prop_correct))

ggplot(cor_by_age_by_site, aes(age_numeric,mean, col = site)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position=position_dodge(width=.2)) +
  geom_point(data = cor_by_age_by_site_by_indiv, aes(x=age_numeric, y=avg_cor), position=position_jitterdodge(jitter.width = NULL,
  jitter.height = .001,
  dodge.width = 0.2,
  seed = 123), alpha=.05) +
  theme_few(base_size = base_size_chosen) +
  labs(x='Age (in years)', y='Proportion drawings recognized') +
  ylim(-.01,1.1) +
  geom_smooth(span=1, alpha=.1) +
  scale_color_viridis(discrete=TRUE, name="", option='B', begin=0, end=.4) +
  theme(legend.position = 'bottom') +
  geom_hline(yintercept = 1/12, linetype="dashed", color="grey")

@@

```{r plot-effort}
## Make compiled plot of descriptives
base_size_chosen=14 # size of text in plots
smooth_alpha=.2

@@

```{r tracing, fig.env="figure", out.width = "\\textwidth", fig.pos = "H", fig.align = "center", fig.width=8, fig.height=4, fig.cap = "Average tracing scores across age and site; each dot represents an average tracing score obtained for each participant and are slightly jittered. Error bars represent bootstrapped 95 percent confidence intervals."} 
ggplot(tracing_scores, aes(x=age_numeric,y=mean, col=site)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
  geom_jitter(data = tracing_scores_indiv, aes(x=age_numeric, y=avg_tracing_score), width=.2, height=.05, alpha=.5) +
  theme_few(base_size = base_size_chosen) +
  labs(x='Age', y='Tracing score') +
  theme(legend.position = "none") +
  geom_smooth(col='grey', span = 10,alpha=smooth_alpha)  +
  facet_grid(~site) +
  ylim(0,4) +
  scale_color_viridis(discrete=TRUE, name="", option='B', begin=0, end=.4)
```
```{r example-drawings, fig.env = "figure", out.width="100%", fig.pos = "H", fig.label="exampledetections", fig.cap = "Randomly sampled, highly recognized drawings for each task, category, and geographical site made by 6-year-old children."}
knitr::include_graphics("figs/example_drawings.png")
```

@@

However, while many have sought to examine variation across different cultural contexts in children's drawings [@winner1989can] or cognitive abilities that may be relevant to children's drawing abilities -- including object recognition [@kuwabara2016cultural] -- we note that this is there is substantial variation within different geographical locations and countries that often goes unmeasured [@amir2020cross].  Indeed, this unmeasured variation within sites may lead to the low replicability of some cross-cultural findings [@carstensen2021]. For example, some work has suggested that the distinction between wheat vs. rice farming traditions explains substantial variation in cultural practices within China [@talhelm2014large]. We are caution against a strong interpretation of the observed site differences, and we believe that drawings from children within the same country -- or even area code --  may differ in the very same ways children's drawings differed in this dataset. For example, children across could reasonably differ in the amount of practice they have drawing common object categories. If so, then children who spend more time drawing may simply have more practice communicating about the diagnostic features of different object categories. In future work, surveys that assesses the amount of time that children in many different communities spend drawing outside could address this hypothesis.

>>>>

```{r setup, include = FALSE}
library("papaja")
library(tidyverse)
library(here)
library(assertthat)
library(langcog)
library(ggthemes)
library(knitr)
library(lmerTest)
library(lme4)
library(xtable)
library(viridis)

knitr::opts_chunk$set(fig.crop = FALSE, 
                      fig.path='figs/', echo=FALSE, warning = FALSE, 
                      cache=FALSE, message = FALSE, sanitize = TRUE)
```

@@

@@

```{r load-tracing}
# import, standardized spliced session_ids, and join back together
# tracing IDs are read in by session_ids, so need these to join with metadata
tracing_thu <- read.csv(here::here('data/compiled/tracing_outputs/transformed_tracings.csv'))  %>%
  mutate(session_id =  paste0('Tsinghua_photodraw_',session_id)) %>%
  filter(site=='Tsinghua') %>%
  left_join(meta_thu, by=c('session_id','category')) %>%
  dplyr::select(-X.1, -X, -site.x, -filename.y) %>%
  rename(site = site.y, filename = filename.x)

@@

```{r check-drawing-time}
# drawing_time <- lmer(draw_duration ~ condition*scale(age_numeric)*site +
#                       (1 | unique_ids) +
#                       (1 | category),
#       data = d)
# drawing_time_out = summary(drawing_time)
```

@@

@@

```{r plot-effort, include=FALSE}
## Make compiled plot of descriptives
base_size_chosen=14 # size of text in plots
smooth_alpha=.2

@@

```{r tracing, fig.env="figure", out.width = "\\textwidth", fig.pos = "H", fig.align = "center", fig.width=8, fig.height=4, fig.cap = "Average tracing scores across age and site; each dot represents an average tracing score obtained for each participant and are slightly jittered. Error bars represent bootstrapped 95 percent confidence intervals."} 
ggplot(tracing_scores, aes(x=age_numeric,y=mean, col=site)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
  geom_jitter(data = tracing_scores_indiv, aes(x=age_numeric, y=avg_tracing_score), width=.2, height=.01, alpha=.5) +
  theme_few(base_size = base_size_chosen) +
  labs(x='Age', y='Tracing score') +
  theme(legend.position = "none") +
  geom_smooth(col='grey', span = 10,alpha=smooth_alpha)  +
  facet_grid(~site) +
  ylim(-.1,4.1) +
  scale_color_viridis(discrete=TRUE, name="", option='B', begin=0, end=.4)
```

```{r example-drawings, fig.env = "figure", out.width="100%", fig.pos = "H", fig.label="exampledetections", fig.cap = "Randomly sampled, highly recognized drawings for each task, category, and geographical site made by 6-year-old children."}
knitr::include_graphics("figs/example_drawings.png")
```

@@

However, while many have sought to examine variation across different cultural contexts in children's drawings [@winner1989can] or cognitive abilities that may be relevant to children's drawing abilities -- including object recognition [@kuwabara2016cultural] -- we note that this is there is substantial variation within different geographical locations and countries that often goes unmeasured [@amir2020cross].  Indeed, this unmeasured variation within sites may lead to the low replicability of some cross-cultural findings [@carstensen2021]. For example, some work has suggested that the distinction between wheat vs. rice farming traditions explains substantial variation in cultural practices within China [@talhelm2014large]. We thus caution against a strong interpretation of the observed site differences, as we believe that drawings from children within the same country -- or even area code --  may differ in the very same ways children's drawings differed in this dataset. For example, children across could reasonably differ in the amount of practice they have drawing common object categories. If so, then children who spend more time drawing may simply have more practice communicating about the diagnostic features of different object categories. In future work, surveys that assesses the amount of time that children in many different communities spend drawing outside could address this hypothesis.
